Using numerical modelling to investigate temperature and wave exposure as drivers of macroalgal characteristics

### 2019-08-04 morphology_paper.Rmd
general house cleaning. updated all output types

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers of macroalgal characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
geometry: margin=1in
output:
  html_document:
    df_print: paged
  pdf_document:
    fig_caption: yes
    fig_crop: no
    fig_height: 7
    fig_width: 7
  word_document:
    reference_docx: frontiers_template.docx
  html_notebook:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
papersize: A4
tables: yes
fontsize: 10pt
---

@@

```{r Temperature variables plot, echo=FALSE, warning=FALSE, fig.cap='Temperature variables at the collection sites around the Cape Peninsula. Temperature variables include minimum represented by blue dots, mean represented by balc dots, maximum by red dots and whiskers standard deviation.'}
ggarrange(temp_plot, temp_boxplot, common.legend = FALSE, ncol = 2, nrow = 1, labels = c("AUTO"))
```

@@

```{r wave variable processing, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Plots for wave variables
#Annual wave plots

@@

wave_ann_meta <- merge(meta_all, wave_ann, by = "site")
wave_ann_meta$site <- as.character(wave_ann_meta$site)

@@

```{r wave variable plot, warming = FALSE, echo=FALSE, message = FALSE, include= TRUE, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers.'}
ggarrange(wave_plot_A,wave_boxplot_1, wave_plot_B, wave_boxplot_2, common.legend = TRUE, labels = c("AUTO"))
```

>>>>

---
title: Using numerical modelling to investigate temperature and wave exposure as drivers of macroalgal characteristics
author: "R. Coppin, C. Rautenbach, T. Ponton and A.J Smit"
geometry: margin=1in
output:
  pdf_document:
    fig_caption: yes
    fig_crop: no
    fig_height: 7
    fig_width: 7
  html_document:
    df_print: paged
  word_document:
    reference_docx: frontiers_template.docx
  html_notebook:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
papersize: A4
tables: yes
fontsize: 10pt
---

@@

```{r Temperature variables plot, echo=FALSE, warning=FALSE,fig.height=7,fig.width=7, fig.cap='Temperature variables at the collection sites around the Cape Peninsula. Temperature variables include minimum represented by blue dots, mean represented by balc dots, maximum by red dots and whiskers standard deviation.'}
ggarrange(temp_plot, temp_boxplot, common.legend = FALSE, ncol = 2, nrow = 1, labels = c("AUTO"))
```

@@

```{r wave variable processing, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
### Plots for wave variables
#Annual wave plots
#combine with meta data for easier plotting
wave_ann_meta <- merge(meta_all, wave_ann, by = "site")
wave_ann_meta$site <- as.character(wave_ann_meta$site)#make character to ensure no issues arise for site and region names

@@

@@

```{r wave variable plot, warming = FALSE, echo=FALSE, message = FALSE, include= TRUE,fig.height=7,fig.width=7, fig.cap='Wave variables at each collection site around the Western Cape coast. Mean variables are represented by dots and standard deviation by whiskers.'}
ggarrange(wave_plot_A,wave_boxplot_1, wave_plot_B, wave_boxplot_2, common.legend = TRUE, labels = c("AUTO"))
```
